Flexibility of interactions depends on habitat suitability

### 2019-08-30 paper/manuscript.Rmd
Start writing intro

@@

<!-- Variation in community composition can be independent of variation of ecological interactions, suggesting that species and inter- action distribution may well respond to diferent drivers (Poisot et al. 2012). -->

@@

>>>>

From a mutualistic perspective, ecological interactions are thought to be selected based on the relative benefit they provide. 
On one end of the spectrum, generalist are have traits that allow them to intract a large number of species.
In average, the benefits they obtain from each of the species they interact with is relatively low compared to specialists.
This is so because, on the other end of the spectrum, specialist species tend to have a have deeper co-evolutionary history with their partner species. 
This in turn is reflected on a better trait-matching with the species it interacts with which leads to a higher benefit.

The 
At the same time, we know that ecological interactions are affected by the environment [@tylianakis_ecological_2017]. 
Generally speaking,

It is generally agreed that two species wether two species interact there is a neutral process

 small number of partner species are thought to benefit largely from each  deeper co-evolutionary history that, through trait matching
Species with a small number of partners, specialists, are often deemed to 
Species with a large number of interactions, generalists, benefits relatively

It is generally accepted that the species niche is the location in a multidimentional space defined by environmental conditions that allows a species to have a positive growth rate when rare (Godsoe). 
There are two dimensions of a species niche, the Grinellian niche which focuses on the

@@

<!-- Variation in community composition can be independent of variation of ecological interactions, suggesting that species and inter- ac tion distribution may well respond to diferent drivers (Poisot et al. 2012). -->

@@

Note that although abundances can inflence wether two species interact we cannot tease t appart because suitability is not necessarily related to abundance. ALthough abundance affects the frequency of the interaction, rather than wether they interacts or not (Donoso)
